---
title: "Sample_project_29/05"
author: "Vinay Raj .N"
date: "`r Sys.Date()`"
output: html_document
---


```{r}
library(dygraphs)
library(plotly)
library(xts)
library(tidyverse)
```

```{r}
# Example -1 simple time series 
```{r}
Nile_ts <- as.xts(Nile)
dygraph(Nile_ts, main = "Nile River Flow")
```

```


```{r}
"city_day.csv" %>% 
  read_csv() %>% 
  select(c(Date,NO)) %>% 
  dygraph(main = "NO Timeseries") %>% 
  dyRangeSelector()
```



```{r}
# Example-2 :Add Range selector 
# Step 1: Convert 'Nile' to xts object
Nile_ts <- as.xts(Nile)

# Step 2: Create dygraph with range selector
nile_graph <- dygraph(Nile_ts, main = "Nile River Flow") %>%
  dyRangeSelector()

# Step 3: Display the graph
nile_graph

```

```{r}
#  Example -3 : Multiple series 

data<- cbind(mdeaths,fdeaths)
data_xts <- as.xts(data)
dygraph(data_xts,main = "Deaths iin the UK ") %>% 
  dySeries("mdeaths",label = "Male") %>% 
  dySeries("fdeaths",label="Female") %>% 
  dyOptions(colors = c("blue","red")) %>% 
  dyRangeSelector()
```
```{r,echo=FALSE}
lungDeathsm <- cbind(mdeaths,fdeaths) 
  dygraph(as.xts(lungDeathsm),main="comaparing deaths of male and female") %>% 
  dySeries("mdeaths",color='darkblue',label = "Male") %>% 
  dySeries("fdeaths",color='tomato',label = "Female") %>% 
  dyHighlight(highlightCircleSize = 5,highlightSeriesBackgroundAlpha =0.2) %>% 
  dyOptions(drawPoints = TRUE,pointSize = 2) %>% 
  dyLegend(show = "auto") %>% # "auto","always","follow"
    dyRangeSelector()

```
```{r}
# -------------------------------------------------------------------
# section 3 :plotly (interactive layer on ggplot)
#--------------------------------------------------------------------
  
# Example-1: Convert ggplot  to plotly 
  mtcars
ggplot(mtcars,aes(x=wt,y=mpg,color = factor(cyl)))+
    geom_point(size=3)+
    labs(title = "Miles per Gallon vs weight ",
         x="weight",y="mpg")->plot_p
ggplotly(plot_p)
```
```{r}
# Example -2
plot_ly(data = mpg, x = ~class, type = "histogram")

```

